Fast and scalable Gaussian process modeling of stellar variability \vspace{-3\baselineskip}

### 2016-09-03 paper/ms.tex
Figure added to Appendix ala Ambikasaran (2015).

\facility{Kepler}
\software{%
    % \project{ceres} \citep{Agarwal:2016},
    % \project{corner.py} \citep{Foreman-Mackey:2016},
    % \project{emcee} \citep{Foreman-Mackey:2013},
    % \project{george} \citep{Ambikasaran:2016},
	% \project{matplotlib} \citep{Hunter:2007},
	% \project{numpy} \citep{Van-Der-Walt:2011},
	% \project{scipy} \citep{Jones:2001}.
}

@@

{\bf Should I give some examples of this?  Some pseudocode? Some colored matrices like Figures 1-2?}

>>>>

\facility{Kepler}
\software{%
    % \project{ceres} \citep{Agarwal:2016},
    % \project{corner.py} \citep{Foreman-Mackey:2016},
    % \project{emcee} \citep{Foreman-Mackey:2013},
    % \project{george} \citep{Ambikasaran2016},
	% \project{matplotlib} \citep{Hunter:2007},
	% \project{numpy} \citep{Van-Der-Walt:2011},
	% \project{scipy} \citep{Jones:2001}.
}

@@

The matrix has a similar structure as the real case constructed by \citep{Ambikasaran2015}, but the
imaginary and real components mix (this is due to the representation of imaginary numbers as
$2\times 2$ matrices).  Figure \ref{matrix_structure} shows an example of the structure of the extended
matrix for two Lorentzians with non-zero $\omega$ values.  This is analagous to the real case with
$p=2$ which also has four additional equations for each row of the original kernel.  This matrix shows
that there is an extra band above and below the diagonal \citep[compare with Figure 2 of][]{Ambikasaran2015}.

\begin{figure}[!htbp]
\begin{center}
\includegraphics[scale=0.175]{./twoterm.eps}
\hspace{0.2in}
\includegraphics[scale=1.0]{./images/colorcode.eps}
\end{center}
\caption{Pictorial description of the extended sparse matrix where $N=10$, $p_0=0$, and $p=2$, following
the example shown in \citet{Ambikasaran2015}.}
\label{matrix_structure}
\end{figure}

{\bf Should I give some examples of this?  Some pseudocode?}
